MINOS Handover Plots

### 2023-07-13 minos/validation/handovers.Rmd
Revert "Merge branch '249_gee' of https://github.com/Leeds-MRG/Minos into 249_gee"
This reverts commit 9b14862ee861227563f95cd9aa374a570765f848, reversing
changes made to 9b764bff3730cdcdaee92edd8f337762bb80f60b.

require(tidyverse)
require(ggplot2)
require(knitr)
require(here)

@@

spaghetti_plot(income.spag, 'hh_income',
               save = shall.we.save,
               save.path = save.path)

>>>>

require(tidyverse)
require(ggplot2)
require(ggridges) # for densities over time plots. 
require(knitr)
require(here)

@@

spaghetti_plot(income.spag, 'hh_income',
               save = shall.we.save,
               save.path = save.path)
density_ridges(income.spag, 'hh_income',
               save=TRUE, 
               save.path=save.path)
